First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-20 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
add the DVCS exclusive selection part in the coherent prl paper

The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
labortory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
factor polarized electrons into three experimental Halls (A, B, C). The data 
were collected over three months via projecting a 6.064 GeV longitudinally 
ploarized beam, (83$\%$ polarization), on a 6 atm gasous $^4$He target.  The 
Hall-B Large Acceptance Spectrometer (CLAS) basic desing \cite{CLAS_ref} was 
upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
with a specially designed electromagnetic calorimeneter, Inner calorimeter 
(IC). The IC has extended the photon detection acceptance of CLAS, which is 
origionally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
the target to shield the inner detectors from the low-energy M\o ller 
electrons.

At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
while the CLAS spectrometer detects charged particles with a threshold of 250 
MeV/c. In order to ensure the exculsitivy of the our coherent DVCS channel, we 
built a small and light radial time projection chamber (RTPC) to detect 
recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
our cylinderical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
$^4$He gaseous target, with a 3 cm radial drift length. The detector was 
specifically calibrated for $^4$He nuclei using elastic scattering produced 
with a 1.2~GeV electron beam.

@@

To ensure that the process is exclusive, we apply cuts on several kinematic 
variables (figure~\ref{fig:kin-cuts}) such as missing energy,
mass and momentum. The cuts are chosen to represent consistently 3 half width 
at half maximum in order to avoid any bias in the selection.

%DVCS selection
\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{ The coherent DVCS exclusivity cuts. The black
distributions represent the coherent DVCS events candidate. The shaded
distributions represent the events which passed all the exclusivity cuts
except the quantity plotted. The vertical red lines represent $3\sigma$ cuts.}
\label{fig:kin-cuts}
\end{figure}

>>>>

The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
laboratory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
factor polarized electrons into three experimental Halls (A, B, C). The data 
were collected over three months via projecting a 6.064 GeV longitudinally 
polarized beam, (83$\%$ polarization), on a 6 atm gaseous $^4$He target.  The 
Hall-B Large Acceptance Spectrometer (CLAS) basic design \cite{CLAS_ref} was 
upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
with a specially designed electromagnetic calorimeter, Inner calorimeter (IC).  
The IC has extended the photon detection acceptance of CLAS, which is 
originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
the target to shield the inner detectors from the low-energy M\o ller 
electrons.

At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
while the CLAS spectrometer detects charged particles with a threshold of 250 
MeV/c. In order to ensure the exclusivity of the our coherent DVCS channel, we 
built a small and light radial time projection chamber (RTPC) to detect 
recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
our cylindrical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
$^4$He gaseous target, with a 3 cm radial drift length. The detector was 
specifically calibrated for $^4$He nuclei using elastic scattering produced 
with a 1.2~GeV electron beam.

@@

%DVCS selection
Identifying the coherent DVCS candidates is the first step of the data 
analysis. These are the events with one electron, one $^4$He, and at least one 
photon in the final state. Electrons were identified by passing the fiducial 
cuts and having signals in all the sub-detectors of CLAS spectrometer (drift 
chambers, Cherenkov counters, the standard CLAS electromagnetic calorimeter, 
and scintillators). $^4$He tracks were identified by passing all the 
geometrical, timing and quality cuts in the RTPC detector. The most energetic 
IC photon was considered as the DVCS photon candidate. Next, a 
$Q^{2}~>~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
ensure that the interaction occurs at the partonic level and the applicability
of the factorization in the DVCS handbag diagram. One the three final state 
particles were identified with their 3-momentum vectors, the exclusivity of the 
coherent DVCS events were ensured by applied a set of 3$\sigma$ exclusivity 
cuts. The exclusive cuts are: the co-planarity angle ($\Delta \phi$), missing 
energy, missing mass squared and missing transverse momentum in the 
$e'~^4He'~\gamma~X$ final state configuration, the missing mass squared in the 
$e'~^4He'~X$ and $e'~\gamma~X$ configurations, and finally the cone angle 
($\theta$) between the measured real photon and the missing particle in the 
$e'~^4He'~X$ configuration. Figure~\ref{fig:kin-cuts} presents four of the 
applied exclusivity cuts.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{ The coherent DVCS exclusivity cuts. The black
distributions represent the coherent DVCS events candidate. The shaded
distributions represent the events which passed all the exclusivity cuts
except the quantity plotted. The vertical red lines represent $3\sigma$ cuts.}
\label{fig:kin-cuts}
\end{figure}
